\textls[-0]{\thetitle}

### 2023-04-01 lang-design.tex
address an AE reviewer's comment

We present the key ingredients of our design as an extension to the Coq
proof assistant,
though we believe the design could be adapted to other proof assistants such as Lean.
We call our design and implementation \Lang (\underline{f}amily
\underline{\smash{po}}lymorphism for a \underline{\smash{p}}roof assistant).
In this section, we focus on the language design of \Lang.
\cref{sec:coqimpl} describes its implementation as a Coq plugin.

@@

We make the observation
that injectivity and disjointness of existing constructors ought to hold
regardless of future addition of constructors.
%
This insight motivates the design of \emph{partial recursors}, which
power the \lsti{finjection} and \lsti{fdiscriminate} tactics.
Partial recursors are automatically generated for all inductive types
defined with \lsti{FInductive}.

>>>>

We present the key ingredients of our design as an extension to the Coq
proof assistant,
though we believe the design could be adapted to other proof assistants such as Lean.
We call our design and implementation \ac{FPOP}.
In this section, we focus on the language design of \Lang.
\cref{sec:coqimpl} describes its implementation as a Coq plugin.

@@

We make the observation
that injectivity and disjointness of existing constructors ought to hold
regardless of future addition of constructors.
%
This insight motivates the design of \emph{partial recursors}, which
power the \lsti{finjection} and \lsti{fdiscriminate} tactics.
Partial recursors can be automatically generated for inductive types
defined with \lsti{FInductive}.
